Generating and modifying matrices

### 2018-04-19 Analysis/Character_difference/02-Modifying_matrices.Rmd
Added missing links

```{r}
## Simulate a matrix
matrix_norm <- sim.morpho(tree, ncharacters, states = c(0.85,0.15),
    model = "mixed", rates = c(rgamma, rate = 100, shape = 3),
    invariant = FALSE)

## Resimulate it if the consistency index is too low
while(check.morpho(matrix_norm)[2,] < 0.26) {
    matrix_norm <- sim.morpho(tree, ncharacters, states = c(0.85,0.15),
        model = "mixed", rates = c(rgamma, rate = 100, shape = 3),
        invariant = FALSE)
}
```

>>>>

```{r}
## Simulate a matrix
matrix_norm <- sim.morpho(tree, ncharacters, states = c(0.85, 0.15),
    model = "mixed", rates = c(rgamma, rate = 100, shape = 3),
    invariant = FALSE)

## Resimulate it if the consistency index is too low
while(check.morpho(matrix_norm)[2,] < 0.26) {
    matrix_norm <- sim.morpho(tree, ncharacters, states = c(0.85, 0.15),
        model = "mixed", rates = c(rgamma, rate = 100, shape = 3),
        invariant = FALSE)
}
```
